Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-23 paper/structureScene.tex
one sentence on invertibility and energy conservation
rephrase a sentence about the CQT

The wavelet transform $\boldsymbol{}$ of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelets.
Applying pointwise complex modulus to $\boldsymbol{y_1}$ yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t).
\end{equation}
The wavelet scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the CQT has a fixed temporal resolution, constrained by the support of the STFT analyzing window.
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost.
This property allows to observe amplitude modulations at fine temporal scales in the scalogram, down to the minimum scale $2Q_1/\xi_1$ for $\gamma = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$.

@@

\cite{Anden2015}
%The temporal scale $2^{\gamma_2}/\xi_2$ takes $5$ values between $23\,\mathrm{ms}$ and $370\,\mathrm{ms}$.
%The log-frequential scale $\beta$ takes $5$ values between $1/4^{\mathrm{th}}$ of an octave and $4$ octaves, as well as their $5$ "mirror" frequencies,
%according to a geometric sequence.
%In addition, the edge case $\gamma_{\mathrm{fr}} = \infty$ corresponds
%to a log-frequential low-pass filter along $4$ octaves
%according to all $5$ temporal scales $2^{\gamma_2}/\xi_2$.

\begin{equation}
\boldsymbol{\psi_{\gamma_{\mathrm{fr}}, \theta_{\mathrm{fr}}}}(\gamma_1)
= \theta_{\mathrm{fr}} 2^{-\gamma_{\mathrm{fr}}/Q_{\mathrm{fr}}}
\boldsymbol{\psi_{\theta_{\mathrm{fr}}}}( \theta_{\mathrm{fr}}  2^{-\gamma_{\mathrm{fr}}/Q_{\mathrm{fr}}}\gamma_1)
\end{equation}

>>>>

The wavelet transform $\boldsymbol{}$ of an audio signal
$\boldsymbol{x}(t)$ is obtained by convolution with all wavelets.
Applying pointwise complex modulus to $\boldsymbol{y_1}$ yields
the wavelet scalogram
\begin{equation}
\boldsymbol{x_1}(t, \gamma_1)
= \vert \boldsymbol{x} \ast \boldsymbol{\psi_{\gamma_1}} \vert (t).
\end{equation}
The wavelet scalogram bears resemblance to the constant-Q transform (CQT),
which is derived from the short-term Fourier transform (STFT) by averaging the frequency
axis into constant-Q subbands of center frequencies $2^{-\gamma_1/Q}\xi_1$.
Indeed, both time-frequency representations are indexed by time $t$ and log-frequency $\gamma_1$.
However, contrary to the CQT, the wavelet scalogram reaches the Heisenberg
theoretical limit of optimal time-frequency localization across the whole
frequency range, whereas the temporal resolution of the CQT is fixed by the support of the STFT analyzing window.
Therefore, the wavelet scalogram has a better temporal localization at high
frequencies than the CQT, at the expense of a greater computational cost.
This property allows to observe amplitude modulations at fine temporal scales in the scalogram, down to the minimum scale $2Q_1/\xi_1$ for $\gamma = 0$, of the order of $1\,\textrm{ms}$ given the aforementioned values of $Q_1$ and $\xi_1$.

@@

\cite{Anden2015}
Since it operates over a complex-valued input, the filterbank over log-frequencies $\gamma_1$ must cover the whole Fourier spectrum, including negative frequencies and the null frequency, to ensure invertibility and energy conservation.
